Greenhouse gas emissions model - making scenarios

### 2021-11-11 Scenarios_report.Rmd
fugde scenario_mc

@@

for (f in Farms)
  {coln<-paste0("Farm_",f)
   scenarios[which(scenarios$Variable %in% "feeding_system"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"system"])
   }

write.csv(scenarios,"data/farm_scenarios.csv")

@@

```{r monte_carlo_simulation}

GHG_simulation_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios.csv",fileEncoding="UTF-8-BOM")[1:2,],
                                 model_function = ghg_emissions,numberOfModelRuns=10,
                                 functionSyntax = "plainNames")

>>>>

variables_to_update<-c(paste0("N_animal_type_",1:12),"feeding_system","feed_prod_CO2","feed_trans_CO2")

@@

for (f in Farms)
  {coln<-paste0("Farm_",f)
   scenarios[which(scenarios$Variable %in% "feeding_system"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"system"])
   scenarios[which(scenarios$Variable %in% "feed_prod_CO2"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])
   scenarios[which(scenarios$Variable %in% "feed_trans_CO2"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])

   }

write.csv(scenarios,"data/farm_scenarios.csv",row.names = FALSE)

@@

```{r monte_carlo_simulation, warning=FALSE}

GHG_simulation_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios.csv",fileEncoding="UTF-8-BOM"),
                                 model_function = ghg_emissions,numberOfModelRuns=10,
                                 functionSyntax = "plainNames")
